\documentclass[a4paper,12pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage[margin=25mm]{geometry}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{lmodern}
\usepackage{luatexja}
\usepackage{setspace}

\setstretch{1.15}

\titleformat{\section}[block]{\Large\bfseries}{\thesection}{1em}{}



\title{高校英語 基本動詞マスター \\ \large 第1回：重要動詞10語}
\date{}

\begin{document}

\maketitle

\section*{make}

\begin{tcolorbox}[title=語源と原義]
語源：古英語 \textit{macian}「作る・形づくる」\\
原義：素材や要素を組み合わせて何かを作る（=create / produce）
\end{tcolorbox}

\begin{tcolorbox}[title=意味の展開]

\begin{itemize}
  \item make a cake（物理的に作る）
  \item make a decision（意思を固める）
  \item make someone happy（状態を変える）
  \item make it to the station（到達する）
  \item make money（稼ぐ）
\end{itemize}

\end{tcolorbox}

\begin{tcolorbox}[title=例文]

\begin{itemize}
  \item She made a beautiful painting for her friend.
  \item Let’s make a plan before we start.
  \item He made it to the final round.
\end{itemize}

\end{tcolorbox}



\section*{take}

\begin{tcolorbox}[title=語源と原義]
語源：古英語 \textit{tacan}（北欧由来）＝「掴んで持ち去る、捕まえる」\\
原義：何かを手に取って、自分のものにする（→移動・変化の始点）
\end{tcolorbox}

\begin{tcolorbox}[title=意味の展開]

\begin{itemize}
  \item take a photo（写真を撮る）
  \item take medicine（薬を飲む）
  \item take a seat（座る）
  \item take time（時間がかかる）
  \item take care of〜（世話する）
  \item take it easy（気楽にやる）
\end{itemize}

\end{tcolorbox}

\begin{tcolorbox}[title=例文]

\begin{itemize}
  \item Can you take a picture of us?
  \item I took the wrong train this morning.
  \item Please take your time.
\end{itemize}

\end{tcolorbox}



\section*{get}

\begin{tcolorbox}[title=語源と原義]
語源：古ノルド語 \textit{geta}「得る、手に入れる」\\
原義：外部から何かを得る、到達する
\end{tcolorbox}

\begin{tcolorbox}[title=意味の展開]

\begin{itemize}
  \item get a present（プレゼントをもらう）
  \item get home（家に着く）
  \item get sick（病気になる）
  \item get angry（怒る）
  \item get things done（物事を片付ける）
\end{itemize}

\end{tcolorbox}

\begin{tcolorbox}[title=例文]

\begin{itemize}
  \item I got a letter from her yesterday.
  \item He got really angry at the news.
  \item What time did you get home?
\end{itemize}

\end{tcolorbox}



\section*{give}

\begin{tcolorbox}[title=語源と原義]
語源：古英語 \textit{giefan}「与える、渡す」\\
原義：自分のものを他者に移す、譲渡する
\end{tcolorbox}

\begin{tcolorbox}[title=意味の展開]

\begin{itemize}
  \item give a gift（プレゼントを渡す）
  \item give advice（助言する）
  \item give someone a hand（手伝う）
  \item give a speech（スピーチをする）
\end{itemize}

\end{tcolorbox}

\begin{tcolorbox}[title=例文]

\begin{itemize}
  \item I gave him a book for his birthday.
  \item She gave a great speech.
  \item Can you give me a hand?
\end{itemize}

\end{tcolorbox}



\end{document}